Multi-resolution Neural Field Estimation

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
authors edits
a few minor edits

\section{Results}
To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.} 
The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into 161 observations. \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. The spatial cutoff frequency was \dean{??} cycles/mm. Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

>>>>

\section{Results}
To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.} 
The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into 161 observations. \dean{The estimation problem is well-posed since there is less state then observations at each level of the decomposition and basis functions are orthogonal.} \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. The spatial cutoff frequency was \dean{??} cycles/mm. Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
